MSHS COVID-19 Vaccination Summary

### 2022-08-12 MSH Vaccines Administered Hybrid Data Model.Rmd
Update weekly dashboard to use hybrid data model. Currently only includes data through June 2022 until we get more data from Epic team.

# # Determine whether or not to update an existing repo
update_repo <- FALSE

# Import reference data for site and pod mappings
sched_repo_dept_mappings <- read_excel(paste0(
  user_directory,
  "/Weekly Dashboard Doses Administered",
  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))

sched_repo_dept_mappings <- sched_repo_dept_mappings %>%
  select(-`Site (Historical)`, -Notes)

vaccine_admin_dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Vaccines Administered Dept Mappings 2022-07-18.xlsx"))

@@

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI")

@@

```{r Import existing repo and append as needed}
# Import schedule repository and determine last date it was updated
sched_repo_summary <- readRDS(paste0(user_directory,
                                  "/Hybrid Repo Sched & Admin Data",
                                  "/Sched Repo Summary 2020-2021 2022-07-18.RDS")
)

vax_admin_repo_summary <- readRDS(paste0(user_directory,
                                  "/Hybrid Repo Sched & Admin Data",
                                  "/Vaccines Admin Summary Jan-Jun2022 2022-07-18.RDS")
)

@@

# sched_repo_update_date <- date(file.info(sched_repo_file)$ctime)

if (update_repo) {

  # Determine date range of reports to add to repository
  if (sched_repo_update_date == today - 1) {
    new_report_dates <- today - 1
  } else {
    new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
  }

  new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")

  # Find list of reports
  file_list_vacc_sched <- list.files(
    path = paste0(user_directory,
                  "/Epic Auto Report Sched All Status"),
    pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
                     new_report_dates_pattern,
                     ".*.csv",
                     collapse = "|"))

  # Import reports and add a column with report name and report date
  import_new_reports <- map_df(
    file_list_vacc_sched,
    .f = function(x){
      sched_data <- read.csv(
        paste0(user_directory,
               "/Epic Auto Report Sched All Status/",
               x),
        stringsAsFactors = FALSE,
        check.names = FALSE) %>%
        mutate(Filename = x,
               ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
                                    "%Y%m%d"),
               DOB = as.Date(DOB, format = "%m/%d/%Y"),
               `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
               Date = as.Date(Date, "%m/%d/%Y"),
               `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
                                        tz = "", format = "%Y-%m-%d %H:%M %p"),
               `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
               `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
                 `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
    }
  )

  # Filter schedule data from new reports to only keep appointments in latest reports
  sched_data_new_reports <- import_new_reports %>%
    group_by(Date) %>%
    slice_max(ReportDate) %>%
    mutate(Filename = NULL,
           ReportDate = NULL) %>%
    ungroup()

  new_reports_dates <- sort(unique(sched_data_new_reports$Date))

  # Remove vaccine appoints from any overlapping dates in repository and new reports
  sched_repo <- sched_repo %>%
    filter(!(Date >= new_reports_dates[1]))

  # Bind schedule repository and schedule from new reports
  sched_repo <- rbind(sched_repo, sched_data_new_reports)

  # Save new repository
  saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
                             "Auto Epic Report Sched ",
                             format(min(sched_repo$Date), "%m%d%y"), " to ",
                             format(max(sched_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

} else {

  hybrid_repo <- hybrid_repo

}
```

```{r Format and process schedule data}
# # Format and analyze schedule to date for dashboards ---------------------------
# sched_to_date <- sched_repo
# 
# sched_to_date <- sched_to_date %>%
#   # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
#   mutate(
#     # Update timezones to EST if imported as UTC
#     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
#     # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
#     Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
#                   ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
#                          ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
#                                 "Dose 3/Boosters", NA))),
#     # Determine appointment date, year, month, etc.
#     ApptDate = date(Date),
#     ApptYear = year(Date),
#     ApptMonth = month(Date),
#     ApptDay = day(Date),
#     ApptWeek = week(Date),
#     # Clean up department if it is duplicated in that column
#     Department = ifelse(str_detect(Department, ","),
#                         substr(Department, 1,
#                                str_locate(Department, ",") - 1),
#                         Department),
#     # Group arrived, completed, and checked out appts as arrived
#     Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
#                     "Arr", `Appt Status`),
#     # Update appointment status: classify any appts from prior days that are
#     # still in scheduled as No Shows
#     Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
#                      # Correct any appts erroneously marked as arrived early
#                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
#                             Status)),
#     # # Determine whether the vaccine is an adult or pediatric dose
#     # VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
#     #                                    "1468 MADISON HOSP PEDS GEN") |
#     #                    `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
#     #                                               "DOSE 2 PEDIATRIC [1324685]") |
#     #                    Department %in% peds_school_practice_dept,
#     #                  "Peds", "Adult"),
#     # # Determine manufacturer based on immunization field and vaccine type fields
#     # Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
#     #   ifelse(Status2 != "Arr", NA,
#     #          # Any blank immunizations and any peds assumed to be Pfizer
#     #          ifelse(is.na(Immunizations) |
#     #                   VaxType %in% c("Peds"), "Pfizer",
#     #                 # Any immunizations with Moderna in text classified as Moderna
#     #                 ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
#     #                        # Any visiting docs or Johnson and Johnson
#     #                        # immunizations classified as J&J
#     #                        ifelse(str_detect(Department, "VISITING DOCS") |
#     #                                 str_detect(Immunizations,
#     #                                            "Johnson and Johnson"),
#     #                               "J&J", "Pfizer")))),
#     # Determine week number of year
#     WeekNum = format(ApptDate, "%U"),
#     # Determine appointment day of week
#     DOW = weekdays(ApptDate)
#   )
# 
# # Crosswalk sites and department grouper
# sched_to_date <- left_join(sched_to_date, dept_mappings,
#                            by = c("Department" = "Department"))
# 
# sched_to_date <- sched_to_date %>%
#   rename(Site = `New Site`)
# 
# # Determine if there are any missing departments and notify user
# unmapped_dept <- sched_to_date %>%
#   filter(is.na(Site)) %>%
#   select(Department) %>%
#   distinct()
# 
# if(nrow(unmapped_dept) > 0) {
#   stop(paste0("Check department mappings. Missing departments include ",
#               paste(as.vector(unmapped_dept$Department), collapse = ", "),
#               "."))
# }
# 
# # Determine vaccine type (adult vs peds) administered based on department, provider, and age, as appropriate
# sched_to_date <- sched_to_date %>%
#   mutate(
#     # Create a column for age grouper
#     Age_Grouper = ifelse(str_detect(Age, "\\ y.o."), "years",
#                          ifelse(str_detect(Age, "\\ m.o."), "months",
#                                 ifelse(str_detect(Age, "\\ days"), "days",
#                                        "unknown"))),
#     # Convert string with age to numeric
#     Age_Numeric = 
#       ifelse(Age_Grouper == "years",
#              as.numeric(str_extract(Age,
#                                     # pattern = "(?<=Deceased\\ \\().+(?=\\ y.o.)")),
#                                     paste("(?<=Deceased\\ \\()[0-9]+(?=\\ y.o.)",
#                                           "[0-9]+(?=\\ y.o.)",
#                                           sep = "|"))),
#              ifelse(Age_Grouper == "months",
#                     as.numeric(str_extract(Age, "[0-9]+(?=\\ m.o.)")) / 12,
#                     ifelse(Age_Grouper == "days",
#                            as.numeric(
#                              str_extract(Age, "[0-9]+(?=\\ days)")) / 365,
#                            ifelse(Age_Grouper == "unknown", 10000,
#                                   NA_integer_)))),
#     # Determine vaccine type based on department, provider/resource, and age if necessary
#     VaxType = ifelse(
#       `Vaccine Age Group` %in% "Peds" |
#         # MSBI Peds POD
#         `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
#                                    "DOSE 2 PEDIATRIC [1324685]") |
#         # Practics that administer adult and pediatric vaccines
#         (`Vaccine Age Group` %in% "Both" &
#            `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
#            Age_Numeric < 12),
#       "Peds", "Adult"),
#     # Determine manufacturer based on immunization field and vaccine type fields
#     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
#       ifelse(Status2 != "Arr", NA,
#              # Any blank immunizations and any peds assumed to be Pfizer
#              ifelse(is.na(Immunizations) |
#                       VaxType %in% c("Peds"), "Pfizer",
#                     # Any immunizations with Moderna in text classified as Moderna
#                     ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
#                            # Any visiting docs or Johnson and Johnson
#                            # immunizations classified as J&J
#                            ifelse(str_detect(Department, "VISITING DOCS") |
#                                     str_detect(Immunizations,
#                                                "Johnson and Johnson"),
#                                   "J&J", "Pfizer")))),
#     Site =
#       # Roll up any Moderna administered at MSB for YWCA to MSH
#       ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
#              # Manually classify school practices as peds or adolescent for schools administering both
#              ifelse(`Setting Grouper` %in% "School Based Practice" &
#                       VaxType %in% "Peds", "Peds School Based Practice",
#                     ifelse(`Setting Grouper` %in% "School Based Practice" &
#                              VaxType %in% "Adult",
#                            "Adolescent School Based Practice",
#                            Site))),
#     # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
#     Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c("Dose 2"), "Dose 1", Dose),
#     `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
#                                "MSHS Practice", `Setting Grouper`))
# 
# vax_admin_start_date <- min(sched_to_date$ApptDate[
#   which(sched_to_date$Status2 %in% "Arr")])
# 
# vax_admin_end_date <- max(sched_to_date$ApptDate[
#   which(sched_to_date$Status2 %in% "Arr")])

@@

## {.tabset}
### All Patient Settings
```{r Create kable of all doses adminsitered to date}
# Summarize data for dashboard visualizations
summary_all_doses <- hybrid_repo %>%
  group_by(Setting, Site, VaxType) %>%
  summarize(Count = sum(Count, na.rm = TRUE)) %>%
  arrange(Setting, VaxType, -Count) %>%
  pivot_wider(names_from = VaxType,
              values_from = Count) %>%
  ungroup() %>%
  arrange(Setting, Site) %>%
  group_split(Setting) %>%
  # split(.$Setting) %>%
  # relocate(Setting, .after = Site) %>%
  map_df(., function(x) {
    adorn_totals(x, where = "row",
                 name = unique(x$Setting),
                 fill = "MSHS Total")})

@@

  if(!(setting %in% unique(sched_to_date$`Setting Grouper`)) |
     (!(vax_type %in% unique(sched_to_date$VaxType)))) {
    stop(paste0("Check your setting and vaccine type."))
  }

  subset_data <- sched_to_date %>%
    filter(Status2 %in% "Arr",
           `Setting Grouper` %in% setting,
           VaxType %in% vax_type) %>%
    group_by(Site, Dose) %>%
    summarize(Count = n()) %>%
    pivot_wider(names_from = Dose,
                # names_prefix = "Dose ",
                values_from = Count) %>%
    arrange(Site) %>%
    mutate(Total = sum(across(contains("Dose")), na.rm = TRUE),
           across(.cols = where(is.numeric),
                  .fns = ~replace_na(.x, 0))) %>%
    adorn_totals(where = "row",
                 name = "MSHS Total",
                 na.rm = TRUE)

  kable(subset_data,
        format = "html",
        escape = FALSE,
        align = "l",
        digits = 0,
        caption = paste(setting, vax_type,
                        "Vaccine Doses Administered"))%>%
    kable_styling(bootstrap_options = "hover", 
                  font_size = 11,
                  full_width = FALSE) %>%
    row_spec(row = 0,
             background = "#221f72",
             color = "white") %>%
    row_spec(row = nrow(subset_data),
             bold = TRUE,
             italic = TRUE)

@@

setting_kable(setting = "Hospital POD",
              vax_type = "Adult")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds")

@@

setting_kable(setting = "MSHS Practice",
              vax_type = "Adult")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds")

@@

**Data Source**

  Analysis based on Epic schedule data.

@@

**Department Mappings**
```{r Reference tab with data sources and mappings}
dept_mappings_dt <- dept_mappings %>%
  # relocate(`Setting Grouper`) %>%
  relocate(Department, .after = `New Site`) %>%
  relocate(`Vaccine Age Group`, .after = Department) %>%
  rename(Site = `New Site`,
         Setting = `Setting Grouper`,
         `Vaccine Administered` = `Vaccine Age Group`) %>%
  mutate(Setting = ifelse(Setting %in% "School Based Practice",
                          "MSHS Practice", Setting),
         `Vaccine Administered` = ifelse(`Vaccine Administered` %in% "Both",
                                         "Adult & Peds",
                                         `Vaccine Administered`)) %>%
  arrange(Setting, Site, Department)

@@

<!-- ### School Based Practices -->
<!-- ```{r Create tables for school based practice vaccine summary} -->

<!-- setting_kable(setting = "School Based Practice", -->
                       <!--               vax_type = "Adult") -->

<!-- setting_kable(setting = "School Based Practice", -->
                       <!--               vax_type = "Peds") -->

<!-- ``` -->

>>>>

# Determine whether or not to update an existing repo
update_repo <- FALSE

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
  sheet = "Hybrid Dept Mapping")

vax_admin_data_mappings <- dept_mappings %>%
  select(-Department) %>%
  unique()

@@

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network")

@@

```{r Import existing repo and append as needed}
# Import schedule repository daily summary for 2020 and 2021
sched_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Sched Arr Visits 2020-2021 Daily Summary 2022-08-12.RDS"))

# Import vaccine administration repository daily summary for Jan-Jun 2022
vax_admin_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-12.RDS"))

@@

# # Needs to be updated once we start receiving weekly reports
# if (update_repo) {
# 
#   # Determine date range of reports to add to repository
#   if (sched_repo_update_date == today - 1) {
#     new_report_dates <- today - 1
#   } else {
#     new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
#   }
# 
#   new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
# 
#   # Find list of reports
#   file_list_vacc_sched <- list.files(
#     path = paste0(user_directory,
#                   "/Epic Auto Report Sched All Status"),
#     pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
#                      new_report_dates_pattern,
#                      ".*.csv",
#                      collapse = "|"))
# 
#   # Import reports and add a column with report name and report date
#   import_new_reports <- map_df(
#     file_list_vacc_sched,
#     .f = function(x){
#       sched_data <- read.csv(
#         paste0(user_directory,
#                "/Epic Auto Report Sched All Status/",
#                x),
#         stringsAsFactors = FALSE,
#         check.names = FALSE) %>%
#         mutate(Filename = x,
#                ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
#                                     "%Y%m%d"),
#                DOB = as.Date(DOB, format = "%m/%d/%Y"),
#                `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
#                Date = as.Date(Date, "%m/%d/%Y"),
#                `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
#                                         tz = "", format = "%Y-%m-%d %H:%M %p"),
#                `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
#                `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
#                  `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
#     }
#   )
# 
#   # Filter schedule data from new reports to only keep appointments in latest reports
#   sched_data_new_reports <- import_new_reports %>%
#     group_by(Date) %>%
#     slice_max(ReportDate) %>%
#     mutate(Filename = NULL,
#            ReportDate = NULL) %>%
#     ungroup()
# 
#   new_reports_dates <- sort(unique(sched_data_new_reports$Date))
# 
#   # Remove vaccine appoints from any overlapping dates in repository and new reports
#   sched_repo <- sched_repo %>%
#     filter(!(Date >= new_reports_dates[1]))
# 
#   # Bind schedule repository and schedule from new reports
#   sched_repo <- rbind(sched_repo, sched_data_new_reports)
# 
#   # Save new repository
#   saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
#                              "Auto Epic Report Sched ",
#                              format(min(sched_repo$Date), "%m%d%y"), " to ",
#                              format(max(sched_repo$Date), "%m%d%y"),
#                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
# 
# } else {
# 
# }
```

```{r Format and process new immunization data}
# new_immune_data <- unique(data)
# 
# new_immune_data <- left_join(new_immune_data,
#                              vax_admin_data_mappings,
#                              by = c("EPICDEPID" = "EpicID"))
# 
# # Add in logic to check for unmapped departments that need to be added to mapping file
# # Note: This is different than immunizations without a department listed
# 
# new_immune_data <- new_immune_data %>%
#   select(-DOSE) %>%
#   mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
#                       ifelse(str_detect(IMMUNE_NAME, "MODERNA"), "Moderna",
#                              ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
#                                     NA))),
#          VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
#                           "Peds (5-11 yo)",
#                           ifelse(str_detect(IMMUNE_NAME,
#                                             "(\\(6 MONTHS - 4 YEARS\\))"),
#                                  "Peds (6 mo - 4 yo)", 
#                           "Adult (12 yo +)")),
#          Dose = ifelse(str_detect(replace_na(PRC_NAME, ""), "DOSE 1"),
#                        "Dose 1",
#                        ifelse(str_detect(replace_na(PRC_NAME, ""),
#                                          "DOSE 2"), "Dose 2",
#                               ifelse(str_detect(replace_na(PRC_NAME, ""),
#                                                 "(DOSE 3)|(BOOSTER)"),
#                                      "Dose 3/Booster", "Dose 3/Booster"
#                               ))),
#          Date = as.Date(str_extract(IMMUNE_DATE,
#                                     "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
#                         format = "%d-%b-%Y")
#          ) %>%
#   rename(Department = DEPARTMENT_NAME)
# 
# new_immune_data_daily_summary <- new_immune_data %>%
#   filter(!is.na(Department)) %>%
#   group_by(Date, Department, `Setting Grouper`, 
#            Site, `Hospital Roll Up`, 
#            VaxType, Dose, Mfg) %>%
#   summarize(Count = n()) %>%
#   ungroup()
# 
# # Add to existing summary
# hybrid_repo <- rbind(hybrid_repo,
#                      new_immune_data_daily_summary)

vax_admin_start_date <- min(hybrid_repo$Date)
vax_admin_end_date <- max(hybrid_repo$Date)

@@

## {.tabset}
### All Patient Settings
```{r Create kable of all doses adminsitered to date}
# Summarize data for dashboard visualizations
summary_all_doses <- hybrid_repo %>%
  mutate(`Setting Grouper` = ifelse(str_detect(Site, "School Practice"),
                                    "MSHS Practice", `Setting Grouper`)) %>%
  group_by(`Setting Grouper`, Site, VaxType) %>%
  summarize(Count = sum(Count, na.rm = TRUE)) %>%
  arrange(`Setting Grouper`, VaxType, -Count) %>%
  pivot_wider(names_from = VaxType,
              values_from = Count) %>%
  ungroup() %>%
  arrange(`Setting Grouper`, Site) %>%
  group_split(`Setting Grouper`) %>%
  # split(.$Setting) %>%
  # relocate(Setting, .after = Site) %>%
  map_df(., function(x) {
    adorn_totals(x, where = "row",
                 name = unique(x$`Setting Grouper`),
                 fill = "MSHS Total")})

@@

  if(!(setting %in% unique(hybrid_repo$`Setting Grouper`)) |
     (!(vax_type %in% unique(hybrid_repo$VaxType)))) {
    stop(paste0("Check your setting and vaccine type."))
  }

  subset_data <- hybrid_repo %>%
    mutate(`Setting Grouper` = ifelse(str_detect(Site, "School Practice"),
                                    "MSHS Practice", `Setting Grouper`)) %>%
    filter(`Setting Grouper` %in% setting,
           VaxType %in% vax_type)

  if(nrow(subset_data) > 0) {

    subset_data <- subset_data %>%
      group_by(Site, Dose) %>%
      summarize(Count = n()) %>%
      pivot_wider(names_from = Dose,
                  # names_prefix = "Dose ",
                  values_from = Count) %>%
      arrange(Site) %>%
      mutate(Total = sum(across(contains("Dose")), na.rm = TRUE),
             across(.cols = where(is.numeric),
                    .fns = ~replace_na(.x, 0))) %>%
      adorn_totals(where = "row",
                   name = "MSHS Total",
                   na.rm = TRUE)

    kable(subset_data,
          format = "html",
          escape = FALSE,
          align = "l",
          digits = 0,
          caption = paste(setting, vax_type,
                          "Vaccine Doses Administered")) %>%
      kable_styling(bootstrap_options = "hover", 
                    font_size = 11,
                    full_width = FALSE) %>%
      row_spec(row = 0,
               background = "#221f72",
               color = "white") %>%
      row_spec(row = nrow(subset_data),
               bold = TRUE,
               italic = TRUE)

@@

setting_kable(setting = "Hospital POD",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (6 mo - 4 yo)")

@@

setting_kable(setting = "MSHS Practice",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (6 mo - 4 yo)")

### MSHS Hospitals Inpatient & ED
```{r Create tables for Inpatient and ED vaccine summary}

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (6 mo - 4 yo)")

@@

**Data Sources**

*2020 and 2021:*
Data based on arrived visits from Epic schedule data.

*2022:*
Based on vaccines administered across health system using completed immunization orders.

*Epic Immunization Data Considerations:*

*   Immunizations with no associated Department/Epic ID excluded from analysis.
*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
*   Vaccine dose based on Procedure Name field in Epic. Immunizations with ambiguous visit types are categorized as Dose 3/Booster.

@@

**Department Mappings**
```{r Reference tab with data sources and mappings}
dept_mappings_dt <- dept_mappings %>%
  select(-`Hospital Roll Up`) %>%
  relocate(`Setting Grouper`) %>%
  relocate(Site, .after = `Setting Grouper`) %>%
  relocate(`Vaccine Age Group`, .after = EpicID) %>%
  rename(Setting = `Setting Grouper`,
         `Epic ID` = EpicID,
         `Vaccine Administered` = `Vaccine Age Group`) %>%
  mutate(Setting = ifelse(Setting %in% "School Based Practice",
                          "MSHS Practice", Setting),
         `Vaccine Administered` = ifelse(`Vaccine Administered` %in% "Both",
                                         "Adult & Peds",
                                         `Vaccine Administered`)) %>%
  arrange(Setting, Site, Department)

@@
